### 2021-04-09 input/proposal.tex
meow

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{birman1999bimodal, hadzilacos1994modular,
  nedelec2018causal, raynal2013distributed}. However, uniform reliable
broadcast states that \emph{all} correct processes must deliver
broadcast messages. This proves costly in large scale systems
comprising thousands of processes. Instead, we define \emph{scoped
broadcast} where messages reach only interested processes,
significantly reducing generated traffic.

@@

In this section, we propose to dynamically adapt the scopes of \NAMEB
using \NAMEB itself for the sake of efficiency. At any time, a process
decides whether or not it becomes the center (or \emph{source}) of a
scope (or \emph{partition}). Processes must eventually rally the
partition corresponding to their closest source despite concurrent
operations, and dynamic changes in the network.

\noindent In that regard, we introduce \NAME (stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}), a
wait-free reactive protocol for dynamic logical partitioning that
enables adaptive scoped broadcast in dynamic distributed
systems. \NAME's operation guarantees that processes eventually reach
consistent partitioning by efficiently propagating their state
changes. \NAME's overhead actually depends on its operations and
current partitions in the system. In other terms,
\begin{inparaenum}[(i)]
\item when the system becomes quiescent, processes eventually converge to
their respective partition and do not require further communication
afterward; and
\item processes do not pay the price of past partitioning.
\end{inparaenum}

@@

At any time, a process can decide to become a source, hence creating a
new partition in the system by executing an \texttt{Add}
operation. This partition includes at least its source plus
neighboring processes that estimate they are closer to this source
than any other source. Such distance (or \emph{weight}) is
application-dependant. For instance, weights could be latency in live
streaming applications, or differences in profiles for recommendation
systems.

@@

Unfortunately, processes do not share a common global knowledge of the
network state. For processes to reach consistent partitioning
together, a process becoming a source must notify every process that
is closer to it than any other source. Epidemic
dissemination~\cite{birman1999bimodal} constitutes an efficient
communication pattern to perform such operation. \TODO{More about
  \emph{forwarding}.}

@@

%% However, since processes operate using local knowledge only, generated
%% traffic may be sub-optimal, for processes may receive, deliver, and
%% forward messages emanating from a same source simply because it did
%% not come from the shortest path yet.

%% Transitive relationships ensure that each
%% process gets its closest source while accumulation of weights ensures
%% that messages propagation terminates.

%% Interestingly, while the receipt order of messages does not impact on
%% local control information ($r_b(\alpha_a^{1.5}) \cdot
%% r_b(\alpha_a^{1}) \Leftrightarrow r_b(\alpha_a^{1}) \cdot
%% r_b(\alpha_a^{1.5}) \implies \TODO{d_b(\alpha_a^{1})}$), it impacts on
%% control information broadcast in the network ($r_b(\alpha_a^{1.5})
%% \cdot r_b(\alpha_a^{1}) \implies b_b(\alpha_{b}^{1.5}) \cdot
%% b_b(\alpha_{b}^{1})$ while $r_b(\alpha_a^{1}) \cdot
%% r_b(\alpha_a^{1.5}) \implies b_b(\alpha_a^{1})$).

While only adding logical partitions to the distributed system is
straightforward, removing them introduces additional complexity:
messages of old partitions may stop the notification of best sources,
for former weights are better than the newly received one.

@@

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system, by executing a
\texttt{Del} operation. All processes that belong to this partition
must eventually choose another partition to belong to. In
Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_c$
that respectively include $\{a\}$, and $\{b, c, d\}$. In
Figure~\ref{fig:delA}, Process $a$ deletes its partition. It notifies
all neighboring processes -- here only Process $b$ -- that may belong
to its partition using \NAMEB. Upon receipt, Process $b$ discards the
message $\delta_a$, for the latter does not target the former's
partition. Yet, Process $b$ sends its own partition that may be the
best for Process $a$. Eventually, every processes belong to the same
partition $P_c$.

@@

\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
  Consistent partitioning where each process can \texttt{Add} and
  \texttt{Del} its partition at any time requires 
  \begin{inparaenum}[(i)]
  \item eventual purging of stale notifications, and
  \item eventual delivery of bests partitions.
  \end{inparaenum}
\end{corollary}

>>>>

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{birman1999bimodal, hadzilacos1994modular,
  nedelec2018causal, raynal2013distributed}. However, uniform reliable
broadcast states that \emph{all} correct processes must deliver
broadcast messages. This proves costly in large scale systems
comprising thousands of processes. Instead, we define \emph{scoped
broadcast} where messages reach only interested processes,
significantly reducing generated traffic. \TODO{Epidemic propagation
  and forwarding are well-aligned with scoped broadcast.}

%% Epidemic
%% dissemination~\cite{birman1999bimodal} constitutes an efficient
%% communication pattern to perform such operation. \TODO{More about
%%   \emph{forwarding}.}

@@

In this section, we propose to dynamically adapt the scopes of \NAMEB
using \NAMEB itself for the sake of efficiency. \TODO{States of
  processes change, predicates change over time.} At any time, a
process decides whether or not it becomes the center (or
\emph{source}) of a scope (or \emph{partition}). Processes must
eventually rally the partition corresponding to their closest source
despite concurrent operations, and dynamic changes in the network.

\noindent In that regard, we introduce \NAME (stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}), a
wait-free reactive protocol for dynamic logical partitioning that
enables adaptive scoped broadcast in dynamic distributed
systems. \NAME's operation guarantees that processes eventually reach
consistent partitioning by efficiently propagating their state
changes. \NAME's overhead actually depends on its operations and
current partitions in the system. When the system becomes quiescent,
processes eventually converge to their respective partition and do not
require further communication afterward.

@@

At any time, a process can decide to become a source, hence creating a
new partition in the system by executing an \texttt{Add}
operation. This partition includes at least its source plus
neighboring processes that estimate they are closer to this source
than any other source. Such distance (or \emph{weight}) is
application-dependant: in the context of maintaining distributed
indexes, weights are latency.

%For instance, weights could be latency in live
% streaming applications, or differences in profiles for recommendation
%systems.

@@

Unfortunately, processes do not share a common global knowledge of the
network state. For processes to reach consistent partitioning
together, a process becoming a source must notify every process that
is closer to it than any other source, using \NAMEB for the sake of
efficiency.

@@

While only adding logical partitions to the distributed system is
straightforward, removing them introduces additional complexity.

@@

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system, by executing a
\texttt{Del} operation. All processes that belong to this partition
must eventually choose another partition to belong to. In
Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_d$
that respectively include $\{a\}$, and $\{b, c, d\}$. In
Figure~\ref{fig:delA}, Process $a$ deletes its partition. It notifies
all neighboring processes -- here only Process $b$ -- that may belong
to its partition using \NAMEB. Upon receipt, Process $b$ discards the
message $\delta_a$, for the latter does not target the former's
partition. Yet, Process $b$ sends its own partition that may be the
best for Process $a$. Eventually, every processes belong to the same
partition $P_d$.

@@

\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
  Consistent partitioning where each process can \texttt{Add} and
  \texttt{Del} its partition at any time requires
  \begin{inparaenum}[(i)]
  \item eventual purging of stale notifications, then
  \item eventual delivery of bests partitions.
  \end{inparaenum}
\end{corollary}
